\newpage
\subsection{Teams }\label{sec:teams}
\figref{fig:sciopsorg} introduces several teams some of which were not in the original ops proposal. A little detail is given here about each.

\subsubsection{Observatory Science}
As in the ops proposal the primary responsibility of this team is to understand the end-to-end impact of the Observatory hardware and environment on the science images and to work with the Observatory \gls{Operations} department to ensure that the image quality meets requirements.

\textbf{This team may be better placed  in Observatory operations department }

\subsubsection{Science algorithms and pipelines}
This team is responsible to assess and assure the alert stream and annual data releases.
In the submitted proposal this includes extensive \gls{QA} to compare the data products against requirements -
this may be be better merged with System Performance/Verification.

The main responsibility  of this team  would then be the  underlying \gls{software} pipelines themselves.
That would include monitoring and updating the \gls{calibration} plan and algorithmic implementation. The Calibration Support Scientist on the Observatory Science team will be responsible for monitoring the physical implementation of the \gls{calibration} plan at the summit.
In \tabref{tab:FTE} this team is initially sized similarly to the AP/DRP teams in construction. There will be significant maintenance in the first two or three years of operations. As mentioned above there may be some consolidation with \gls{QA} activities in System Performance.

\subsubsection{Science platform  }
This team will be responsible for maintaining and evolving LSST’s user access portal, the \gls{Science Platform}. This will include keeping up with evolving technologies and computing infrastructure, as well as providing basic code-base maintenance, bug fixes, and low-level response to science community and internal \gls{LSST} requests for new features.

\subsubsection{Middleware }
In a service oriented model with a layered architecture as outlined in \secref{sec:arc} it is essential to have a cross cutting team who compose and debug services.
Software such as the \texttt{butler}  is not part of the \gls{pipeline} but the \gls{pipeline} needs it. In house developments such as \gls{Qserv} should be covered here (1.5FTE has been included for this those are  DOE/SLAC personnel, it could be 2FTE).
This would also cover the builds and how the code interacts with the infrastructure (\secref{sec:infra}.

\subsubsection{Infrastructure, Site Reliability Engineering  } \label{sec:infra}
This is for deployment of of various systems and pipelines. Configuration is included in this. There needs to be a couple of people who manage keys/secrets
for access to commodity services. We would need a security resource as well as database expertise.  This then implies using tooling for system management as
provided by e.g. \gls{AWS} console.

In general an \gls{SRE} team is responsible for the availability, latency, performance, efficiency, change management, monitoring, emergency response and capacity planning of their services \cite{Beyer:2016:SRE:3006357}.

This team would include paying for a liaison at any service provider e.g. Google Professional Services or a Service Manager at \gls{NCSA}. (2FTE calculated)

\subsubsection{Verification/Operations }
This team will take and verify new releases for operations before they are deployed to the operations system. They will monitor the operational system to make sure it is functioning - they should have some science knowledge to know it is actually working properly as opposed to not just giving errors. A team of 4 should be able to handle this.
Some support for this is assumed from IN2P3 .
